---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

```

# previewbw


A lot of plots are made while assuming that the audience will see the plot in
colors. However, articles are often printed in black and white and these plots
are thus unreadable.

The goal of `previewbw` is to show what a plot will look like if it's printed in
black and white, so that the person who made the plot can adapt it to be readable
in black and white. The preview will be in lower quality but that should still be
enough to assess whether the plot is readable.

## Installation

You can install the development version of previewbw like so:

``` r
devtools::install_github("etiennebacher/previewbw")
```

## Example

Here are a few examples coming from `ggpubr` and `see` (I don't have anything 
against these packages, they just provide a lot of examples that I can use):

```{r}
library(previewbw)
library(effectsize)
library(see)
library(ggpubr)

t_to_d(t = c(1, -1.3, -3, 2.3), df_error = c(40, 35, 40, 85)) %>%
  equivalence_test(range = 1) %>%
  plot()

previewbw()
```

```{r}
set.seed(1234)
wdata <- data.frame(
   sex = factor(rep(c("F", "M"), each=200)),
   weight = c(rnorm(200, 55), rnorm(200, 58)))

ggdensity(wdata, x = "weight",
   add = "mean", rug = TRUE,
   color = "sex", fill = "sex",
   palette = c("#00AFBB", "#E7B800"))

previewbw()
```

```{r}
data("mtcars")
dfm <- mtcars
dfm$cyl <- as.factor(dfm$cyl)
dfm$name <- rownames(dfm)

ggbarplot(dfm, x = "name", y = "mpg",
          fill = "cyl",              
          color = "white",            
          palette = "jco",            
          sort.val = "desc",          
          sort.by.groups = FALSE,     
          x.text.angle = 90          
          )

previewbw()
```

